---
title: "Presentation of Linear Models in Shiny"
author: "Gergely Horvath"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
mpgData <- mtcars[, c("mpg", "disp")]
faithfulData <- faithful
```

## Datasets

On the left side of the screen there is a selectInput widget which the user may use to select the dataset to be charted.

The available datasets are:

```{r}
head(mtcars[, c("mpg", "disp")], 2)
```

```{r}
head(faithful, 2)
```


## Scatter Plot & Linear Model

After selection of a dataset, the scatterplot is automatically updated as it is 'reactive'. 

If the check box "Draw Regression Line" is selected by the user, then a Linear Model is calculated and the regression line is drawn as seen on the next page.

This page is located at: https://greg1717.github.io/p09_dev_data_prod/week_3_plotly.html

***
```{r}
plot(mpg ~ disp, data = mpgData)
lm1 <- lm(mpg ~ disp, data = mtcars)
abline(lm1)
```

***

```{r}
plot(eruptions ~ waiting, data = faithfulData)
lm1 <- lm(eruptions ~ waiting, data = faithfulData)
abline(lm1)
```
