---
title: "Swirl - Week 4"
author: "Gergely"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(swirlify)
new_lesson("Lesson 1", "My First Course")
```

> library(swirlify)
> new_lesson("Lesson 1", "My First Course")
Creating new lesson in /Users/gergely/Documents/coursera/data_science/p09_dev_data_prod/My_First_Course/Lesson_1
If the lesson file doesn't open automatically, you can open it now to begin editing...
> wq_message()
> wq_command()
> add_to_manifest()
> test_lesson()
##### Begin testing: Lesson 1 #####
##### End testing: Lesson 1 #####

> demo_lesson()

| Course installed successfully!

  |                                                                                                                             |   0%

| Welcome to Lesson 1!


# Multiple Options

get_current_lesson()

```{r}
new_lesson("Lesson 2", "My First Course")
wq_multiple()
add_to_manifest()
test_lesson()
demo_lesson()
```

# Figure Type Question

```{r}
wq_figure()
# figure will come from an R script
# figure type "new" or "add"
```

